|

### 2022-06-14 article.qmd
sending articles qmd 13

```{python}
descr.__get__(self,obj,type=None)-->value
descr.__set__(self,obj,value)-->None
descr.__delete__(self,obj)-->None

@@

En faisant 
```{python}
val = Mydecriptor()

@@

```{python}
class Myclass():
val = MyDescriptor("val") 
```
> C'est pas pratique de taper le nom manuellement à chaque instanciation, n'est ce pas !

@@

```{python}
class Person(object):
    id = PrimaryKeyField()
    name = VarCharField(max_lenght=255)

>>>>

```Python
descr.__get__(self,obj,type=None)-->value
descr.__set__(self,obj,value)-->None
descr.__delete__(self,obj)-->None

@@

En faisant 
```Python
val = Mydescriptor()

@@

```Python
class Myclass():
val = MyDescriptor("val") 
```
> C'est pas pratique de taper le nom manuellement à chaque instanciation, n'est ce pas !

@@

```Python
class Person(object):
    id = PrimaryKeyField()
    name = VarCharField(max_lenght=255)
